IGRINS spectra of \name

### 2016-03-24 document/ms.tex
more prose on methodology approach 1

The model $\vM(\vT)$ as it stands only models a single set of stellar parameters for the entire wavelength range of interest.  This model is the desired beavior for most applications involving a single stellar photospheric component.  In our case, however, we \emph{know} that a single stellar photospheric component is a poor model for the data: there are \emph{two} components lurking in the composite spectrum.

>>>>

The model $\vM(\vT)$ was intended to apply a single set of stellar parameters to the entire wavelength range of interest, presumably the entire available spectrum.  For a spectrum from a multi-order echelle spectrograph, this means each spectral order is fit with the same stellar parameters.  Simultaneous fitting is the desired behavior for most applications involving a single stellar photospheric component.  In our case, however, we know that a single stellar photospheric component is a poor model for the data: there are \emph{two} components lurking in the composite spectrum.  But depending on the star spot properties, a single stellar photosphere component might fit the composite spectrum satisfactorily, like if the flux contrast of the starspot is simply too low compared to the noise.

The starspot contrast depends on wavelength, roughly as the ratio of blackbodies.  Figure XX shows a plot of the flux ratio of two stellar photospheres with identical stellar properties except for different effective temperatures.  So a sufficiently large bandwidth spectrum could exhibit differing levels of fit quality as a function of wavelength, if a single temperature photosphere fit is naively applied to different chunks of wavelengths.

We modified the \iancze spectral inference framework to fit $\vM$ in each spectral order \emph{independently}: $\vT \rightarrow \vT_o$, where $o$ signifies the spectral order, which could stem from multiple spectrographs, each with multiple orders.  This change does not represent reality: the star has a single set of stellar properties, which do not depend on the wavelength range at which they are measured.  The naive single-component fit to different wavelength chunks conveys information about

\begin{eqnarray} \label{eqn:scaling}
\vM(\vT_o) &=& \vM(\vt_{\ast}, \vt_{\rm ext}) \\
         &=& \vM(\vt_{\ast}, \sigma_v, v\sin{i}, v_r) \times \Omega \times 10^{-0.4\,A_{\lambda}}, \nonumber
\end{eqnarray}

star spot areal coverage fraction is very small, then the signal associated with the
